A fault tolerant multi-server system for MMOGs

### 2010-10-28 textos/phd-prospectus/prospectus.tex
writing

\usepackage[utf-8]{inputenc}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposed Model} \label{sec_model}
%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

when adding a large number of players (falar aqui de timeliness), specially if they are distributed among different servers, many questions become critical. (falar aqui da sincroniza‹o com varios servidores)

- direct communication (players -> signed -> check by servers)

>>>>

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposed Model} \label{sec:model}
%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The next sections will describe the services the service must provide to the players connected to it (Section \ref{sec:services}), the specific requirements for a fault-tolerant distributed MMOG server system, considering the crash-stop failure model, and the proposed distributed architecture (Section \ref{sec:feats}) and an algorithm devised to synchronize the game state between the replicas (Section \ref{sec:algorithm}).

\subsection{Services to be provided} \label{sec:services}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Characteristics and architecture of the intended distributed game server system} \label{sec:feats}

The main purpose of the system is to reduce or, ideally, eliminate the necessity of a central server for the game. In this work, the approach proposed to achieve this is based on principles similar to those of volunteer computing, where a potentially large set of contributors make their computers available to perform tasks requested by some remote entity. With such a system, although each of these nodes is probably much less powerful than a traditional mmog server, when working together they can sum up the cpu power and network link necessary to host one of these games.

However, several questions arise when dealing with a potentially large scale geographically distributed server system composed of voluntary nodes. First, as the nodes are volunteer, there is no guarantee that they will be available whenever they are needed, neither there is any guarantee regarding the amount of resources that each of these nodes makes available for the system -- be it cpu power, network bandwidth or storage. Besides, not only can these nodes become unavailable, but there can be a high rate of nodes joining and leaving the system, characterizing churn. There are also problems related to the geographical distribution of this system, as the option of using efficient group communication techniques -- such as network level multicast -- is not widely available on the Internet. Finally, considering the potentially large number of nodes in this system, it is very likely that some of them present failures, for what we are assuming the crash-stop failure model -- therefore, we assume the possibility of nodes crashing and network links becoming unavailable.

%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Proposed architecture} \label{sec:arch}

%x

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Proposed synchronization algorithm} \label{sec:algorithm}

y

%%%%%%%%%%%%%%%%%%%%%%%%%
começar a falar das características específicas do sistema servidor distribuído, o que ele deve fazer (replicação, sincronização, tolerância a falhas, modelo crash-stop)

when adding a large number of players (falar aqui de timeliness), specially if they are distributed among different servers, many questions become critical. (falar aqui da sincronização com vários servidores)

- direct communication (players -> signed -> check by servers OU )
